\chapter{建议信}

\section{2012英I}

\noindent Dear Students,

Welcome to our university for further study. On behalf of the Students' Union, I am 
writing this email in order to offer some [advice/suggestions/proposals/tips]
[about/concerning/with regards to] campus life. 

[Much can be shared./ Relevant advice can be [summarized/outlined] as follows.]
More specifically, it is wise to [grasp/master] some basic Chinese expressions in advance
so that you are able to overcome language barriers during the process of learning.
In addition, you are adviced to take part in various social activities in your spare time to 
make new friends. Finally, were I you, I would download WeChat into smartphones to communicate with 
classmates and teachers conveniently.

I wish that you could accept my advice, expecting your arrival.

\YSLM

\section{2021英I}

\noindent Dear Friend,

How is it going recently? I am greatly delighted to hear that you are going to 
take up an occupation in China, writing this email \dots 

In addition, you are advised to prepare a detailed CV(简历) to highlight 
your advantages, including your educational background, working experience 
and other related skills.
Finally, were I you, I would download job-hunting apps into the smartphone to 
gain some information about openings. 

\YSLM

\newpage 

\section{2011英II}

Dear Li Ming,

Congratulations. I am greatly delighted to hear that \dots, writing \dots 

More specifically, it is wise to concentrate on learning and keep away from 
online games so that you are able to improve the competitive edge in the future.
In addition, \dots Finally, you must [form/develop/cultivate] a sense of independence in life.

I wish that you could accept my advice, expecting your reply.

\YSLM

\section{2016英II}

\noindent Dear Jack,

Thanks for your congratulations. I am writing this email in order to \dots

In addition, you are adviced to take part in some translation courses to gain related skills.
Finally, \dots download translation apps to check your translation content conveniently.

\section{2014英I}

\noindent Dear President, 

As a senior student in this university, I am writing this email to offer some porposals about how to 
imporve students' physical well-being.

Relevant details can be outlined as follows. More specifically, it is necessary to enhance students'
awareness of doing exercise which can contribute to student's health. 
In addition, our college is expected to purchase updated sports [equipment/facilities] to [spark/fuel] 
sutdents' passion for doing exercise. 
Finally, we would appreciate it if our canteen could provide more nutritionally balanced diets.

I wish that you could take my advice into [account/consideration], expecting your positive reply.

\YSLM

\chapter{邀请信}

\noindent \Attention{时间/地点}/目的/主题/内容/收获/要求

\section{2022英II}

\noindent Dear Students,

A campus food festival, which is organized by XXX, is around the corner.
Thus, I am writing this email in order to invite you to take part in this activity.

Much can be shared. More specifically, the festival will be held on the playground on May 1,
from 8:00 am to 8:00 pm. In addition, the purpose of this festival is to help you gain deeper 
understanding of Chinese fool culture.
Finally, you will have chances to taste various delicious snacks. 

I wish that you could take my invitation into [account/consideration], expecting your positive reply.

\YSLM

\section{2021英II}

Finally, you are adviced to download Ding Talk in advanced and participate in the meeting on time.

\section{2013英II}

In addition, the purpose of this charity sale in to help children from disadvantaged families
finish their schooling.
Finally, you are expected to bring something for sale and raise money to help those kids in need.

\newpage

\section{2013英I}

\dots to act as a judge for the contest.

In addition, the contest will consist of three rounds and select 10 winners in the end.
Finally, you are expected to assess candidates's performance 
and share some tips concerning English learning.

\chapter{推荐信}

\section{2011英I}

\noindent Dear Friend,

Knowing that you [enjoy/are fond of/are fascinated with] watching films in your spare time,
I am writing this email in order to recommend a great masterpiece - \textit{Away}. 

Much can be shared. More specifically, the film tells a moving and inspiring story: a boy
experiences countless difficulties and achieves success in the end.
In addition, the film will spark your passion for life when you feel depressed. 
Finally, the film can help you gain deeper understanding of the culture of 
the British society and culture. 

I wish that you could take my recommendation into [account/consideration], expecting your positive reply.

\YSLM

\section{2015英I}

\noindent Films $ \Rightarrow $ Books

\section{2017英I}

More specifically, it is a good idea to visit the local museun in which you will 
have chances to gain deeper understanding of history and culture. 
In addition, you can go to Liu Gong Island to experience the fishers' life.
Finally, if you are interesting in delicious food, the Walking Street is strongly recommended.

\newpage

\section{2023英II}

\noindent Dear David,

Knowing that \dots, I am writing this \dots

Were I you, I would go \dots More specifically,
the XXX can help you gain deeper understanding of \dots
In addition, you will have chances to appreciate \dots
Finall, you are likely to make new friends who have common interest with you.

\chapter{介绍信}

\section{2017英II}

\noindent Dear Professor Williams,

I am more than honored to accept your invitation, writing this email in order to specify the main 
points of my presentation. 

Much can be shared. More specifically, the first part of my presentation will involve an outstanding 
Chinese philosopher - Lao Zi - and his thought called Taoism that has dramatic effects on Chinese culture.
In addition, the second part will center on Chinese tea culture and its difference from other tea cultures.
Finally, time permitted, I will display some videos about Chinese Kung Fu.

I wish my presentation could spark students' passion for Chinese culture, 
expecting your positive reply.

\YSLM

\section{2019英I}

\noindent Dear Friend,

I am greatly delighted to receive your letter, writing \dots

Much can be shared. More specifically, the purpose of this project is to help
children from disadvantaged families finish schooling.
In addition, besides raising money for those kids, the project also enlists college 
students to act as volunteers in rural primary schools. 
Finally, volunteers who are fluent in English are badly needed in 
the project. 

I wish that my introduction could be useful for you, expecting your participation in our project.

\YSLM

\chapter{低频类型}

\section{感谢信 - 2010英II}

\noindent Dear Jack,

I have just returned to my home, writing this email with the purpose of expressing my 
gratitude for your hospitality and inviting you to visit China.

Much can be said. Thanks to your help, I could get used to foreign life and 
overcome language barriers during the process of communiation. 
Moreover, I have gained deeper understanding of culture difference. 
In return for your help, I sincerely invite you to visit my country. 
I will show you around my city and you will have chances to taste various
delicious snacks.

All in all, words fail to express my gratitude. I am expecting your arrival.

\YSLM

\section{投诉信 - 2012英II}

\noindent To Whom It May Concern,

As a customer who purchased an electronic dictionary from your online store,
I am writing this letter with the purpose of expressing my dissatisfaction
with your product and demanding a reasonable solution.

Much can be complained. More specifically, the battery life falls short of 
my expectation, and I must recharge it frequently. To make matter worse, the
keyboard does not work sometimes, which is extremely annoying. 
As for the solution, I will mail the product back to you for a further check.
If you cannot repair it, you must give me a new one or a full refund.

I do hope that you will give serious thought to my complaint and request,
expecting your attention and action. 

\atRight{Yours,}

\atRight{Zhang Wei}

\section{道歉信 - 2018英II}

\noindent Dear Professor Smith,

I am greatly regretful to tell you that I have to cancel my original plan, 
writing this email with the purpose of making an apology and suggesting a future meeting.

The reason why I change my plan is that I come down with serious flu due to unknown virus.
My doctor requires me to stay in the hospital until full recovery. I wonder whether you have 
available time in August. If you have, I will call on you at that time. 

I am sorry for any inconvenience caused to you, hoping that you could understand my 
situation and accept my apology.

\YSLM

\section{辞职信 - 2005英I}

\noindent Dear Mr.Wang,

Thanks for giving me a working oppotunity two months ago. Unfortunately, 
I find the work is unsuitable for me, writing this email with the purpose of 
quitting my full-time employment.

Relevant reasons can be outlined as follows. More specifically, the salary falls short of my
expectation. As a consequence, as a breadwinner, I suffer from huge economic pressure. To make
matters worse, the task turns out to be challenging and demanding, because I fail to keep 
abreast of the latest trend in fashion. Finally, I decide to pursue further study to boost my 
comprehensive ability. 

I am sorry for any inconvenience caused to you, hoping that you could understand my 
situation and accept my resignation.

\YSLM

\section{请求信 - 2006英I}

\noindent To Whom It May Concern,

As a senior student who intends to help a kid from a rural area, I am 
writing this email with the purpose of seeking your help in 
finding a candidate. 

Relevant requirements can be outlined as follows. To be more specific, the kid should 
come from a disadvantaged family and work diligently. 
Besides, the kid ought to be willing to help others in need.
As for my plan, I will mail 114514 RMB annually to the kid in order to cover 
his or her schooling fees. 

Thanks for your time and effort in advance. I am expecting your positive reply. 

\YSLM

\chapter{通知}

\section{2010英I}

\begin{center}
    NOTICE

    \quad{}\quad{}
    \quad{}\quad{}
    \quad{}\quad{}
    May 1,2023
\end{center}

A significant international conference on globalization will be held in our university 
from May 10 to May 13. Thus, the notice is meant to recurit volunteers for this conference.

Concrete qualifications can be outlined as follows. To be more specific, the 
candidiates should be fluent in English to overcome language barriers during the 
process of communiation. Besides, in terms of personality, the applicants had better be 
outgoing and patient. Finally, students who have related working experience will be given priority.

If you are interesting in this position, please do not hesitate to contact us via 12345678.
We are expecting your active participation.

\atRight{Postgraduate Association}

\section{2023英I}

\begin{center}
    NOTICE

    \quad{}\quad{}
    \quad{}\quad{}
    \quad{}\quad{}
    May 1,2023
\end{center}

Concrete duties can be outlined as follows. To be more specific, the job 
involves data collection and analysis. Besides, the candidate should be 
proficient in processing data. 
Finally, the student who has related working experience will be given priority.

\newpage

\section{2016英I}

\begin{center}
    NOTICE

    \quad{}\quad{}
    \quad{}\quad{}
    \quad{}\quad{}
    May 1,2023
\end{center}

Welcome to our university for further study. The notice is meant to provide you with 
relevant information about the library. 

Concrete details can be outlined as follows. To be more specific, the openings 
hour of our library is from \dots to \dots Besides, your students' cards are needed if 
you intend to enter the library. Finally, we have fashioned a series of rules in order to 
create clean reading surroundings. For instance, drinks and foods are strictly prohibited. 

If you have other questions, please do not hesitate to contact us via \dots
We are expecting your arrival. 

\atRight{Li Ming}

\section{2020英I}

第一段参考邀请信

第二段参考邀请信(2013)

Finally, you are expected to select one of your favorite songs and display your singing talent in 
the contest. 

\chapter{(较难的)建议信}

\section{2019英II}

\noindent Dear Professor Smith,

I am more than honored to be asked to plan a debate, writing this email with the 
purpose of suggesting a specific topic and sharing my arrangement.

I am convinced that the topic concerning bike sharing is suitable, because although some people 
welcome this policy, others strongly object it. Thus, the topic is sure to arouse much debate.
As for concrete arrangement, the debate can be held on Sunday, from 6:00 pm to 9:00 pm in the 
Lecture Hall. 

I wish that you could take my proposal into account, expecting your positive reply. 

\YSLM

