\chapter{小作文}

\section{感谢的小作文}

\noindent Directions:

Soppose you won the first prize in a competition. Your English tutor helped you a lot 
with the preparation. Now \Attention{write} an \underline{email} to express your gratitude.

Write nearly about 100 words on the Answer Sheet.

Don't write your own name. Use "Li Ming" instead.

Don't write the address.

\subsection{看题}

\begin{enumerate}
    \item 注意 write 后接的文体，确认是书信 letter/mail/email/note, 通知告示
    notice/announcement 还是纪要 minutes.
    \item 写 90-110 词左右。
\end{enumerate}

\subsection{开题}

\noindent Dear XXX,

\begin{itemize}
    \item Sir (or Madam) - 完全未知；
    \item President - 职位为编辑、校长、经理等；
    \item Prof. Smith / Mr. Smith - 长辈；
    \item Jack / Mary - 同辈；
    \item Friends / Classmates - 朋友们、同学们。 
\end{itemize}

\subsection{正文}

More than delighted / Shocked to ... , I'm writing this email with 
the purpose of ... .

XXXXXX.

I ..., expecting your reply.

\YTLM

\section{旅游的小作文}

\noindent Dear Sir or Madam, 

Being a senior from a prestigious university[万能], I am planning to go to Europe for 
the 2-week leisure trip with a group, so I am writing to inquire into some information.

\section{重点注意的文章类型}

申请信、推荐人、回复、询问、感谢。

\begin{enumerate}
    \item \textbf{申请信} 
    
    求职、志愿者、加入团队

    \begin{itemize}
        \item I am writing to apply for an opportunity to be a member of ... .
        \item To briefly introduce myself, I am majoring in ... and 
        expect graduaction next June. Secondly, not only do I have excellent 
        academic performance in all courses, I also possess rich working 
        experience. Plus, my interactive skills and team spirit are also 
        appropriate for this post.
    \end{itemize}

    推荐他人可以照改。
    \item \textbf{回复}
    
    未能完成的任务、未能达成的承诺、未能赴约的邀请 - 致歉 + 原因。

    I have entered for the Postgraduate Entrance Examination and the test is coming in very few days. 
    I am fully occupied with reviewing all the books as well as materials. You know, it is of great 
    importance to me because it tightly concerns my future career.
    \item \textbf{询问}
    
    \begin{itemize}
        \item What are the dates between which ... will be held and what are the daily opening hours?
        \item Is there any discount for students or is it for free?
        \item Would you please ... ?
    \end{itemize} 
\end{enumerate}

\chapter{大作文}

\section{作文主题}

一定不考社会热点；考学生的素养或习惯，或者文化问题。


\begin{itemize}
    \item \textbf{品质} - 独立、合作、乐观、自信、选择、行动、坚持
    
    重要点：\begin{itemize}
        \item 独立性 independence 
        \item 合作 cooperation, cllaboration 
        \item 乐观 optimism, positive attitude
    \end{itemize}

    未考：\begin{itemize}
        \item 创新 innovation, creativity, initiative 
        \item 工匠精神 the spirit of craftmanship
    \end{itemize}
    \item 科技 - 科技负面性
    \item 公德 - 爱心、亲情、素质
    
    小爱：亲情、友情、爱情、邻里关系、同学关系

    大爱：对社会，奉献爱心；对\textbf{自然}，低碳生活。
    \item 时间 - 学习、读书、\textbf{锻炼}
    \item 文化 - 文化
\end{itemize}

\sssubsection{运动}

sneakers/sports shoes

so as to enjoy better life quality and longevity.

Doing sports will greatly increase people's immune system, and 
strengthen our physical conditions. 
Sports also help to refresh people's mind from brain work all day and night.
More surprisingly, exercising ... 

\sssubsection{科技负面}

There is no denying that digital products have brought much convenience to our routine life. 
Meanwhile, a lot of time has been wasted. However, for me, the time can be fully used 
to do something more meaningful, such as doing exercises. 

\sssubsection{低碳生活}

低碳生活 develop the low-carbon lifestyle / 厉行节约 practice economy
/ cultivate the awareness of environmental protection 培养保护意识

The fast growing economy gives rise to a series of problems, among which 
serious ones are the excessive emission of carbon dioxide and the waste of resources.
In such a case, they inevitably in turn cause more negative effects. As a result, 
the earth is in danger and it is high time to XXX. It can not only help save 
energies and cut down the pollution, but also leave adequate resources to 
our following generations. 